 

### 2019-07-26 Manuscript/Manuscript R1/SupplementaryMaterial.Rmd
Update old version

---
title: " "
author: |
bibliography: CircularData.bib
csl: apa.csl
output:
  pdf_document:
    fig_caption: yes
    keep_tex: yes
    latex_engine: pdflatex
    number_sections: no
fontsize: 12pt
geometry: margin=1in
header-includes:
  - \usepackage{multirow}
  - \usepackage{appendix}
  - \usepackage{color}
  - \usepackage{hyperref}
  - \usepackage{subcaption}
  - \setlength\parindent{24pt}
  - \usepackage{setspace}\doublespacing
documentclass: article
pandoc_args: --natbib
---

>>>>

---
title: " "
author: |
bibliography: CircularData.bib
csl: apa.csl
output:
  pdf_document:
    fig_caption: yes
    keep_tex: yes
    latex_engine: pdflatex
    number_sections: no
fontsize: 12pt
geometry: margin=1in
header-includes:
  - \usepackage{multirow}
  - \usepackage{appendix}
  - \usepackage{color}
  - \usepackage{hyperref}
  - \usepackage{subcaption}
  - \setlength\parindent{24pt}
  - \usepackage{setspace}\doublespacing
  - \DeclareRobustCommand{\VANDER}[3]{#2} 
  - \DeclareRobustCommand{\VAN}[3]{#2}
  - \DeclareRobustCommand{\DEN}[3]{#2}
documentclass: article
pandoc_args: --natbib
---
